### 2019-03-20 response/response-demography-1.tex

The only downside is that I had to remove the confidence intervals for legibility. 
I, therefore, still include Tables 1-3, but have moved them to the Appendix, and I have 
added the probability of a birth to the tables.
I have also combined the 75th, 50th, and 25th percentiles results tables in the Appendix.

\item 10. As sex composition and sex ratios has been examined in the literature, I think
it would make sense to not present findings on that in great detail. As
the paper states, the central question addressed is spacing, and so all
other questions should not be dealt in detail

[Response:]

As detailed above, I have refocused the Results section to focus mainly on birth spacing
and how that is affected by the increased use of sex selection over time.
I now instead refer to the previous literature on sex ratios and use that as a guide for
structuring the analysis of birth spacing.

@@

\item 11. The results talk about compression of spacing. This is important and
literature on it should be presented in the intro or lit review section.
There is evidence of compression of the reproductive span at least in
some regions (see Padmadas, et. Al 2004). It would be important to
consider how this fits in with the results presented.

[Response:]
Compression in the original manuscript was only for first birth, and I no longer cover 
those because of the data issues discussed above.
I do, however, agree that this is an important question, even if I cannot directly
address it here.
I, therefore, have added this to the conclusion when I discuss areas of future research.

### 2019-03-21 paper/sex_selection_spacing-ver2.tex
Minor edits

Figure \ref{fig:pps_low} shows the distribution of birth within a spell for women with no 
education.
For the second spell, what is most interesting is that there is almost no difference 
between those with a first-born boy and those with a first-born girl.
For the 1972--1984 period the two conditional survival curves only begin to diverge 
at around 18 months (corresponding to 27 months after the first birth took place), and
at that point close to 50 percent of the women have already had their second child.
The literature on birth spacing and child health suggests that an interpregnancy interval
of less than 18 months is associated with a higher risk of adverse health outcomes and
mortality \citep{Conde-Agudelo2012}.
With a nine-month pregnancy this means that almost 50 percent of the children born fall
in this category, and, somewhat surprisingly, that there do not appear to be any particular 
disadvantage for the child born after a girl than after a boy.%
\footnote{
Note that this does not imply that the first-born girl is not in a more adverse position
than a first-born boy when the second child arrives.
}
The difference in spacing between a first-born girl and a first-born boy first-born 
remains almost the same across the four decades.
Furthermore, the proportion with very short spacing remains almost the same.

>>>>

Figure \ref{fig:pps_low} shows the distribution of birth within a spell for women with no 
education.
For the second spell, what is most interesting is that there is almost no difference 
between those with a first-born boy and those with a first-born girl.
For the 1972--1984 period the two conditional survival curves only begin to diverge 
at around 18 months (corresponding to 27 months after the first birth took place), and
at that point close to 50 percent of the women have already had their second child.
The literature on birth spacing and child health suggests that an interpregnancy interval
of less than 18 months is associated with a higher risk of adverse health outcomes and
mortality \citep{Conde-Agudelo2012}.
With a nine-month pregnancy this means that almost 50 percent of the children born fall
in this category, and, somewhat surprisingly, that there do not appear to be any particular 
disadvantage for the child born after a girl than after a boy.%
\footnote{
Note that this does not imply that the first-born girl is not in a more adverse position
than a first-born boy when the second child arrives, just that this is not directly
related to a short birth interval.
}
The difference in spacing between a first-born girl and a first-born boy first-born 
remains almost the same across the four decades.
Furthermore, the proportion with very short spacing remains almost the same.
